---
title: "Results"
author: "Shubila Balaile"
date: '2021-04-12'
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,fig.width=10, fig.height=6)
#clear the global environment
rm(list = ls(all.names = TRUE))

library(tidyverse)
library(readxl)
library(tidyverse)
library("mlr")
library("iml")
library("future")
library("future.callr")
library("ggplot2")
library(gridExtra)



# load partial featimp objects

#load("../output/ml_object/caret/partial/logit_partial_featimp_ce.RData")
#load("../output/ml_object/caret/partial/rf_partial_featimp_ce.RData")
#rename_pred <- read_excel("../documentation/Rename_predictors.xlsx",sheet = "Rename",col_names = TRUE)
load("../output/ml_object/caret/partial/test_train_partial_data.RData")
#load("../output/ml_object/caret/partial/logit_partial_model.RData")
load("../output/ml_object/caret/partial/rf_partial_model.RData")


```

## Results - Feature Importance


The permutation feature importance algorithm based on Fisher, Rudin, and Dominici (2018):

Input: Trained model f, feature matrix X, target vector y, error measure L(y,f).

1.Estimate the original model error eorig = L(y, f(X)) (e.g. mean squared error)  
2.For each feature j = 1,...,p do:  
   Generate feature matrix Xperm by permuting feature j in the data X. This breaks the association between feature j and true outcome y.  
  Estimate error eperm = L(Y,f(Xperm)) based on the predictions of the permuted data.    
  Calculate permutation feature importance  
  FIj= eperm/eorig.   
  Alternatively, the difference can be used:   
  FIj = eperm - eorig
3.Sort features by descending FI.

## Results - Pdp:s versus Ales for predictors of importance using the caret model object

The partial function tells us for given value(s) of features S what the average marginal effect on the prediction is.

```{r G1, echo=FALSE}



predictor_rf    = Predictor$new(rf_train_output_partial, data = lgbti_partial_train, class = "Open",type = "prob")


pdp_rf    = FeatureEffect$new(predictor_rf, "G1_A", method = "pdp")
ale_rf    = FeatureEffect$new(predictor_rf, "G1_A", method = "ale")


plot_pdp_ale <- function(feature,lab,effpdp,effale,model) {
  
  feature  <- rlang::enquo(feature)
  feature2 <- quo_name(feature)
  
  eff_rf_pdp    <- effpdp$results %>%
  mutate(model = {{model}}) %>%
  filter(.type == "pdp")
  
  eff_rf_ale    <- effale$results %>%
  mutate(model = {{model}}) %>%
  filter(.type == "ale") %>%
    mutate({{feature}} := fct_relevel({{feature}},levels=levels(eff_rf_pdp[,!!feature2])))
    
  
  plot_pdp <- eff_rf_pdp %>%
  ggplot(., aes(x = {{feature}}, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(eff_rf_pdp$.type)) +
  xlab(lab) +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

  plot_ale <- eff_rf_ale %>%
  ggplot(., aes(x = {{feature}}, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(eff_rf_ale$.type))+
  xlab(lab) +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )
  
  
  plot_comb <- gridExtra::grid.arrange(plot_pdp, plot_ale, ncol = 1, top = model)
  
  
  return(plot_comb)
}


df_pdp_ale <- function(feature,lab,effpdp,effale,model) {
  
  

 feature  <- rlang::enquo(feature)
 feature2 <- quo_name(feature)
  
  eff_rf_pdp    <- effpdp$results %>%
  mutate(model = {{model}}) %>%
  filter(.type == "pdp")
  
  eff_rf_ale    <- effale$results %>%
  mutate(model = {{model}}) %>%
  filter(.type == "ale") %>%
    mutate({{feature}} := fct_relevel({{feature}},levels=levels(eff_rf_pdp[,!!feature2])))
  
  
  list_df <- list(eff_rf_pdp,eff_rf_ale)
  
  return(list_df)
}



G1_A <- plot_pdp_ale(feature = G1_A, lab = "open_fam",effpdp = pdp_rf ,effale = ale_rf ,model = "caret" )

G1_A

################## G1_B #####################

pdp_rf$set.feature("G1_B")
ale_rf$set.feature("G1_B")

G1_B <- plot_pdp_ale(feature = G1_B, lab = "open_friend",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

G1_B

################## G1_C #####################

pdp_rf$set.feature("G1_C")
ale_rf$set.feature("G1_C")

G1_C <- plot_pdp_ale(feature = G1_C, lab = "open_neigh",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

G1_C

################## G1_E #####################

pdp_rf$set.feature("G1_E")
ale_rf$set.feature("G1_E")

G1_E <- plot_pdp_ale(feature = G1_E, lab = "open_stud",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

G1_E


################## G1_H #####################

pdp_rf$set.feature("G1_H")
ale_rf$set.feature("G1_H")

G1_H <- plot_pdp_ale(feature = G1_H, lab = "open_med",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

G1_H




```


```{r work, echo=FALSE}

################## C7_B #####################

pdp_rf$set.feature("C7_B")
ale_rf$set.feature("C7_B")

C7_B <- plot_pdp_ale(feature = C7_B, lab = "work_supp",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

C7_B

################## C6_1_D #####################

pdp_rf$set.feature("C6_1_D")
ale_rf$set.feature("C6_1_D")

C6_1_D <- plot_pdp_ale(feature = C6_1_D, lab = "work_gen_neg", effpdp = pdp_rf ,effale = ale_rf ,model = "caret")


C6_1_D


```


```{r sch_hide, echo=FALSE}

pdp_rf$set.feature("C8_B")
ale_rf$set.feature("C8_B")

sch_hide <- plot_pdp_ale(feature = C8_B, lab = "sch_hide",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

sch_hide
 


```





```{r empl, echo=FALSE}

pdp_rf$set.feature("H2")
ale_rf$set.feature("H2")


empl_pdp <- df_pdp_ale(feature = H2, lab = "empl",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[1]]%>%
  mutate(H2 = fct_recode(H2,
                                "Paid work"   = "In paid work",
                                "Self-empl"   = "Self-employed",
                              "Unpaid work"   = "Unpaid/voluntary work",
                              "Unemployed"    = "Unemployed",
                              "Student"       = "Student or pupil",
                              "Retired"       = "Retired",
                              "Unable"        = "Unable to work-health problems",
                            "Domestic task"   = "Domestic tasks",
                            "Mili/Civil serv" = "Military/Civilian service",
                            "Other"           = "Other"
                           )
         )

empl_ale <- df_pdp_ale(feature = H2, lab = "empl",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[2]] %>%
  mutate(H2 = fct_recode(H2,
                                "Paid work"   = "In paid work",
                                "Self-empl"   = "Self-employed",
                              "Unpaid work"   = "Unpaid/voluntary work",
                              "Unemployed"    = "Unemployed",
                              "Student"       = "Student or pupil",
                              "Retired"       = "Retired",
                              "Unable"        = "Unable to work-health problems",
                            "Domestic task"   = "Domestic tasks",
                            "Mili/Civil serv" = "Military/Civilian service",
                            "Other"           = "Other"
                           ),
         H2 = fct_relevel(H2,levels=levels(empl_pdp$H2))
         
         )

plot_empl_pdp <-   empl_pdp %>%
  ggplot(., aes(x = H2, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(empl_pdp$.type)) +
  xlab("empl") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

plot_empl_ale <- empl_ale  %>%
  ggplot(., aes(x = H2, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(empl_ale$.type)) +
  xlab("empl") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

gridExtra::grid.arrange(plot_empl_pdp, plot_empl_ale, ncol = 1,top = "caret")


```


```{r avoid_hands, echo=FALSE}


pdp_rf$set.feature("D1")
ale_rf$set.feature("D1")

avoid_hands_pdp <- df_pdp_ale(feature = D1, lab = "avoid_hands",effpdp = pdp_rf ,effale = ale_rf ,model =  "caret")[[1]]
avoid_hands_ale <- df_pdp_ale(feature = D1, lab = "avoid_hands",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[2]]%>%
mutate(D1 = fct_relevel(D1,levels=levels(avoid_hands_pdp$D1))
)

plot_avoid_hands_pdp <-   avoid_hands_pdp %>%
  ggplot(., aes(x = D1, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(avoid_hands_pdp$.type)) +
  xlab("avoid_hands") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

plot_avoid_hands_ale <-   avoid_hands_ale %>%
  ggplot(., aes(x = D1, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(avoid_hands_ale$.type)) +
  xlab("avoid_hands") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

gridExtra::grid.arrange(plot_avoid_hands_pdp, plot_avoid_hands_ale, ncol = 1,top = "caret")

```




```{r age, echo=FALSE}


pdp_rf$set.feature("A1")
ale_rf$set.feature("A1")

age <- plot_pdp_ale(feature = A1, lab = "age",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

age


```






```{r resp_cat, echo=FALSE}


pdp_rf$set.feature("RESPONDENT_CATEGORY")
ale_rf$set.feature("RESPONDENT_CATEGORY")

resp_cat_pdp <- df_pdp_ale(feature = RESPONDENT_CATEGORY, lab = "resp_cat",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[1]]

resp_cat_ale <- df_pdp_ale(feature = RESPONDENT_CATEGORY, lab = "resp_cat",effpdp = pdp_rf ,effale = ale_rf ,model="caret")[[2]]%>%
mutate(RESPONDENT_CATEGORY = fct_relevel(RESPONDENT_CATEGORY,levels=levels(resp_cat_pdp$RESPONDENT_CATEGORY))
)

plot_resp_cat_pdp <-   resp_cat_pdp %>%
  ggplot(., aes(x = RESPONDENT_CATEGORY, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(resp_cat_pdp$.type)) +
  xlab("resp_cat") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

plot_resp_cat_ale <-   resp_cat_ale %>%
  ggplot(., aes(x = RESPONDENT_CATEGORY, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(resp_cat_ale$.type)) +
  xlab("avoid_hands") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

gridExtra::grid.arrange(plot_resp_cat_pdp, plot_resp_cat_ale, ncol = 1,top = "caret")




```




```{r ctry, echo=FALSE}

pdp_rf$set.feature("A10")
ale_rf$set.feature("A10")

ctry_pdp <- df_pdp_ale(feature = A10, lab = "ctry",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[1]] %>%
  mutate(A10 = fct_recode(A10,
                                "AT"   = "Austria",
                                "BE"   = "Belgium",
                                "BG"   = "Bulgaria",
                                "HR"   = "Croatia",
                                "CY"   = "Cyprus",
                                "CZ"   = "Czech Republic",
                                "DK"   = "Denmark",
                                "EE"   = "Estonia",
                                "FI"   = "Finland",
                                "FR"   = "France",
                                "DE"   = "Germany",
                                "GR"   = "Greece",
                                "HU"   = "Hungary",
                                "IE"   = "Ireland",
                                "IT"   = "Italy",
                                "LV"   = "Latvia",
                                "LT"   = "Lithuania",
                                "LU"   = "Luxembourg",
                                "MT"   = "Malta",
                                "NL"   = "Netherlands",
                                "PL"   = "Poland",
                                "PT"   = "Portugal",
                                "RO"   = "Romania",
                                "SK"   = "Slovakia",
                                "SI"   = "Slovenia",
                                "ES"   = "Spain",
                                "SE"   = "Sweden",
                                "UK"   = "United Kingdom",
                                "MK"   = "North Macedonia",
                                "RS"   = "Serbia"
                            )
         )

ctry_ale <- df_pdp_ale(feature = A10, lab = "ctry",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")[[2]] %>%
  mutate(A10 = fct_recode(A10,
                                "AT"   = "Austria",
                                "BE"   = "Belgium",
                                "BG"   = "Bulgaria",
                                "HR"   = "Croatia",
                                "CY"   = "Cyprus",
                                "CZ"   = "Czech Republic",
                                "DK"   = "Denmark",
                                "EE"   = "Estonia",
                                "FI"   = "Finland",
                                "FR"   = "France",
                                "DE"   = "Germany",
                                "GR"   = "Greece",
                                "HU"   = "Hungary",
                                "IE"   = "Ireland",
                                "IT"   = "Italy",
                                "LV"   = "Latvia",
                                "LT"   = "Lithuania",
                                "LU"   = "Luxembourg",
                                "MT"   = "Malta",
                                "NL"   = "Netherlands",
                                "PL"   = "Poland",
                                "PT"   = "Portugal",
                                "RO"   = "Romania",
                                "SK"   = "Slovakia",
                                "SI"   = "Slovenia",
                                "ES"   = "Spain",
                                "SE"   = "Sweden",
                                "UK"   = "United Kingdom",
                                "MK"   = "North Macedonia",
                                "RS"   = "Serbia"
                            ),
          A10 = fct_relevel(A10,levels=levels(ctry_pdp$A10))
         )



plot_ctry_pdp <-   ctry_pdp %>%
  ggplot(., aes(x = A10, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(ctry_pdp$.type)) +
  xlab("ctry") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

plot_ctry_ale <-   ctry_ale %>%
  ggplot(., aes(x = A10, y =.value,group = .type)) +
  geom_line(aes(group = .type)) +
  ggtitle(unique(ctry_ale$.type)) +
  xlab("ctry") +
  ylab("predicted probability")+
  theme(
    plot.title = element_text(size = 10)
  )

gridExtra::grid.arrange(plot_ctry_pdp, plot_ctry_ale, ncol = 1,top = "caret")



```


```{r satisf, echo=FALSE}

pdp_rf$set.feature("G2")
ale_rf$set.feature("G2")

satisf <- plot_pdp_ale(feature = G2, lab = "satisf",effpdp = pdp_rf ,effale = ale_rf ,model = "caret")

satisf

```

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```

