---
title: "Results"
author: "Shubila Balaile"
date: '2021-04-12'
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,fig.width=10, fig.height=6)
#clear the global environment
rm(list = ls(all.names = TRUE))

library(tidyverse)
library(readxl)
library(tidyverse)
library("mlr")
library("iml")
library("future")
library("future.callr")
library("ggplot2")
library(gridExtra)



# load partial featimp objects

load("../output/ml_object/caret/partial/logit_partial_featimp_ce.RData")
load("../output/ml_object/caret/partial/rf_partial_featimp_ce.RData")
rename_pred <- read_excel("../documentation/Rename_predictors.xlsx",sheet = "Rename",col_names = TRUE)
load("../output/ml_object/caret/partial/test_train_partial_data.RData")
load("../output/ml_object/caret/partial/logit_partial_model.RData")
load("../output/ml_object/caret/partial/rf_partial_model.RData")


```

## Results - Feature Importance


The permutation feature importance algorithm based on Fisher, Rudin, and Dominici (2018):

Input: Trained model f, feature matrix X, target vector y, error measure L(y,f).

1.Estimate the original model error eorig = L(y, f(X)) (e.g. mean squared error)  
2.For each feature j = 1,...,p do:  
   Generate feature matrix Xperm by permuting feature j in the data X. This breaks the association between feature j and true outcome y.  
  Estimate error eperm = L(Y,f(Xperm)) based on the predictions of the permuted data.    
  Calculate permutation feature importance  
  FIj= eperm/eorig.   
  Alternatively, the difference can be used:   
  FIj = eperm - eorig
3.Sort features by descending FI.

```{r featimp,echo=FALSE, fig.height = 6, fig.width = 8}

# extract the results table from the featimp object

logit_featimp_partial       <- logit_partial_featimp_ce$results

rf_featimp_partial          <- rf_partial_featimp_ce$results 

# join the new names of predictors

logit_featimp_partial <- inner_join(logit_featimp_partial,rename_pred, by = c("feature" = "old"))
rf_featimp_partial    <- inner_join(rf_featimp_partial,rename_pred,    by = c("feature" = "old"))

# how many variables to include in the plot 

number_vars <- 30


# generate logit plot 

plot_logit_featimp <- logit_featimp_partial %>%
  slice_max(importance, n = number_vars) %>%
  ggplot(., aes(importance, reorder(new, importance))) +
  geom_point(size = 2) +
  geom_linerange(aes(xmin = importance.05, xmax = importance.95)) +
  ggtitle("logit") +
  ylab("feature") +
  theme(
        axis.text.y = element_text(size = 8, face = "bold"),
        plot.title = element_text(size = 10)
        )



# generate rf plot 

plot_rf_featimp <- rf_featimp_partial %>%
  slice_max(importance, n = number_vars) %>%
  ggplot(., aes(importance, reorder(new, importance))) +
  geom_point(size = 2) +
  geom_linerange(aes(xmin = importance.05, xmax = importance.95)) +
  ggtitle("randomforest") +
  ylab("feature") +
  theme(
    axis.text.y = element_text(size = 8, face = "bold"),
    plot.title = element_text(size = 10)
  )



(plot_featimp_ce <- gridExtra::grid.arrange(plot_logit_featimp, plot_rf_featimp, nrow = 1))


```

## Results - Partial Dependence Plot with ICE:s

The partial function tells us for given value(s) of features S what the average marginal effect on the prediction is.

```{r G1, echo=FALSE}

#predictor_logit = Predictor$new(logit_train_output_partial, data = lgbti_partial_train, class = "Open")

predictor_rf    = Predictor$new(rf_train_output_partial, data = lgbti_partial_train, class = "Open",type = "prob")


pdp_rf    = FeatureEffect$new(predictor_rf, "G1_A", method = "pdp+ice") 

sample_id <- sample(unique(pdp_rf$results$.id[pdp_rf$results$.type=="ice"]),300)

plotdf_comb <- function(feature,lab) {
  
  
  pdp_rf_ice    <- pdp_rf$results %>%
  mutate(predictor = {{lab}}) %>%
    filter(.id %in% sample_id) %>%
    rename(variable = {{feature}}) 
  
  pdp_rf_pdp    <- pdp_rf$results %>%
  mutate(predictor = {{lab}}) %>%
  filter(.type == "pdp") %>%
    rename(variable = {{feature}}) %>%
    mutate(`.id` = -1L)
    #mutate(`.id` = if_else(is.na(`.id`),-1L,`.id`))
  
  pdp_tab <- rbind.data.frame(pdp_rf_pdp,pdp_rf_ice)
  return(pdp_tab)
}

plotdf_ind <- function(feature,lab) {
  
  
  pdp_rf_ice    <- pdp_rf$results %>%
    mutate(predictor = {{lab}}) %>%
    filter(.id %in% sample_id) %>%
    rename({{lab}} := {{feature}}) 
  
  pdp_rf_pdp    <- pdp_rf$results %>%
    mutate(predictor = {{lab}}) %>%
    filter(.type == "pdp") %>%
    rename({{lab}} := {{feature}}) %>%
    mutate(`.id` = -1L)
  #mutate(`.id` = if_else(is.na(`.id`),-1L,`.id`))
  
  pdp_tab <- rbind.data.frame(pdp_rf_pdp,pdp_rf_ice)
  return(pdp_tab)
}


G1_A <- plotdf_comb(feature = G1_A, lab = "open_fam")

pdp_rf$set.feature("G1_B")
 
G1_B <- plotdf_comb(feature = G1_B, lab = "open_friend")

pdp_rf$set.feature("G1_C")

G1_C <- plotdf_comb(feature = G1_C, lab = "open_neigh")

pdp_rf$set.feature("G1_E")

G1_E <- plotdf_comb(feature = G1_E, lab = "open_stud")

pdp_rf$set.feature("G1_H")

G1_H <- plotdf_comb(feature = G1_H, lab = "open_med")

G1 <- rbind.data.frame(G1_A,G1_B,G1_C,G1_E,G1_H)

ggplot(G1,
       aes(
         x = variable,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
 # facet_wrap(~ predictor) +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))
  


```


```{r work, echo=FALSE}

pdp_rf$set.feature("C7_B")

C7_B <- plotdf_comb(feature = C7_B, lab = "work_supp")

pdp_rf$set.feature("C6_1_D")

C6_1_D <- plotdf_comb(feature = C6_1_D, lab = "work_gen_neg")

work <- rbind.data.frame(C7_B,C6_1_D)

ggplot(work,
       aes(
         x = variable,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  facet_wrap(~ predictor) +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))


```


```{r sch_hide, echo=FALSE}

pdp_rf$set.feature("C8_B")

sch_hide <- plotdf_ind(feature = C8_B, lab = "sch_hide")

ggplot(sch_hide,
       aes(
         x = sch_hide,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))

 


```





```{r empl, echo=FALSE}

pdp_rf$set.feature("H2")

empl <- plotdf_ind(feature = H2, lab = "empl") %>%
  mutate(empl = fct_recode(empl,
                                "Paid work"   = "In paid work",
                                "Self-empl"   = "Self-employed",
                              "Unpaid work"   = "Unpaid/voluntary work",
                              "Unemployed"    = "Unemployed",
                              "Student"       = "Student or pupil",
                              "Retired"       = "Retired",
                              "Unable"        = "Unable to work-health problems",
                            "Domestic task"   = "Domestic tasks",
                            "Mili/Civil serv" = "Military/Civilian service",
                            "Other"           = "Other"
                           )
         )


ggplot(empl,
       aes(
         x = empl,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))

```


```{r avoid_hands, echo=FALSE}


pdp_rf$set.feature("D1")

avoid_hands <- plotdf_ind(feature = D1, lab = "avoid_hands")

ggplot(avoid_hands,
       aes(
         x = avoid_hands,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))

```




```{r age, echo=FALSE}


pdp_rf$set.feature("A1")

age <- plotdf_ind(feature = A1, lab = "age")

ggplot(age,
       aes(
         x = age,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))


```






```{r resp_cat, echo=FALSE}


pdp_rf$set.feature("RESPONDENT_CATEGORY")

resp_cat <- plotdf_ind(feature = RESPONDENT_CATEGORY, lab = "resp_cat")


ggplot(resp_cat,
       aes(
         x = resp_cat,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))



```




```{r ctry, echo=FALSE}

pdp_rf$set.feature("A10")

ctry <- plotdf_ind(feature = A10, lab = "ctry") %>%
  mutate(ctry = fct_recode(ctry,
                                "AT"   = "Austria",
                                "BE"   = "Belgium",
                                "BG"   = "Bulgaria",
                                "HR"   = "Croatia",
                                "CY"   = "Cyprus",
                                "CZ"   = "Czech Republic",
                                "DK"   = "Denmark",
                                "EE"   = "Estonia",
                                "FI"   = "Finland",
                                "FR"   = "France",
                                "DE"   = "Germany",
                                "GR"   = "Greece",
                                "HU"   = "Hungary",
                                "IE"   = "Ireland",
                                "IT"   = "Italy",
                                "LV"   = "Latvia",
                                "LT"   = "Lithuania",
                                "LU"   = "Luxembourg",
                                "MT"   = "Malta",
                                "NL"   = "Netherlands",
                                "PL"   = "Poland",
                                "PT"   = "Portugal",
                                "RO"   = "Romania",
                                "SK"   = "Slovakia",
                                "SI"   = "Slovenia",
                                "ES"   = "Spain",
                                "SE"   = "Sweden",
                                "UK"   = "United Kingdom",
                                "MK"   = "North Macedonia",
                                "RS"   = "Serbia"
                            )
         )


ggplot(ctry,
       aes(
         x = ctry,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))



```


```{r satisf, echo=FALSE}

pdp_rf$set.feature("G2")

satisf <- plotdf_ind(feature = G2, lab = "satisf")

ggplot(satisf ,
       aes(
         x = satisf ,
         y = .value,
         group = .id
       )) +
  geom_line(aes(group = .id, color = .type,
                size = .type, alpha = .type)) +
  geom_rug() +
  ylab("predicted probability") +
  theme(plot.title = element_text(size = 10)) +
  scale_color_manual(values = c("black","red")) +
  scale_size_manual(values = c(0.06, 1.4)) +
  scale_alpha_manual(values = c(0.2, 1))

```

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```

